Efficiently Handling Guards in the Low Level Design of RPython's Tracing JIT

### 2012-08-07 talk/vmil2012/paper.tex
argh

\begin{description}
    \item[chaos:] A Chaosgame implementation creating a fractal.
    \item[crypto\_pyaes:] An AES implementation.
    \item[django:] The templating engine of the Django Web
        framework\footnote{\url{http://www.djangoproject.com/}}.

    \item[go:] A Monte-Carlo Go
        AI\footnote{\url{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}.
    \item[pyflate\_fast:] A BZ2 decoder.
    \item[raytrace\_simple:] A ray tracer.
    \item[richards:] The Richards benchmark.
    \item[spambayes:] A Bayesian spam filter\footnote{\url{http://spambayes.sourceforge.net/}}.
    \item[simpy\_expand:] A computer algebra system.
    \item[telco:] A Python version of the Telco decimal
        benchmark\footnote{\url{http://speleotrove.com/decimal/telco.html}},
        using a pure Python decimal floating point implementation.
    \item[twisted\_names:] A DNS server benchmark using the Twisted networking
        framework\footnote{\url{http://twistedmatrix.com/}}.
\end{description}

>>>>

\begin{description}
    \item[chaos:] A Chaosgame implementation creating a fractal.
    \item[crypto\_pyaes:] An AES implementation.
    \item[django:] The templating engine of the Django Web
        framework.\footnote{\url{http://www.djangoproject.com/}}

    \item[go:] A Monte-Carlo Go
        AI.\footnote{\url{http://shed-skin.blogspot.com/2009/07/ disco-elegant-python-go-player.html}}
    \item[pyflate\_fast:] A BZ2 decoder.
    \item[raytrace\_simple:] A ray tracer.
    \item[richards:] The Richards benchmark.
    \item[spambayes:] A Bayesian spam filter.\footnote{\url{http://spambayes.sourceforge.net/}}
    \item[simpy\_expand:] A computer algebra system.
    \item[telco:] A Python version of the Telco decimal
        benchmark,\footnote{\url{http://speleotrove.com/decimal/telco.html}}
        using a pure Python decimal floating point implementation.
    \item[twisted\_names:] A DNS server benchmark using the Twisted networking
        framework.\footnote{\url{http://twistedmatrix.com/}}
\end{description}
